Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-23 doc/asplos13/abstract.tex
pass on abstract and intro.

Grappa is a latency tolerant runtime system for commodity clusters of
multicore computers, its goal is to provide scalable performance for irregular
parallel applications. These applications are of growing importance as
interactive analysis of large data sets emerges as a commercial and government
priority, typically in the form of graph processing. Grappa serves both as a
C++ user library and as a foundation upon which higher level languages can be
developed or adapted to support development of irregular parallel
applications. Grappa tolerates the delays to distant memory by multiplexing
thousands of lightweight tasks to each processor core; balances load via
fine-grained distributed work-stealing; takes full advantage of network
characteristics by aggregating smaller requests into large ones; and provides
efficient synchronization and remote operations across its single shared
address space. We present a detailed description of the Grappa system,
programming examples using the library interface, and compare performance for
several irregular benchmarks to the Cray XMT, a custom system used to target
the real time graph analytics market.

>>>>

Grappa is a latency tolerant runtime system for commodity clusters of
multicore computers. Grappa's goal is to provide scalable performance for
irregular parallel applications. These applications are of growing importance
as interactive analysis of large data sets emerges as a commercial and
government priority, typically in the form of graph processing. Grappa serves
both as a C++ user library and as a foundation upon which higher level
languages can be developed or adapted to support development of irregular
parallel applications. Grappa tolerates the delays to distant memory by
multiplexing thousands of lightweight tasks to each processor core; balances
load via fine-grained distributed work-stealing; takes full advantage of
network characteristics by aggregating smaller requests into large ones; and
provides efficient synchronization and remote operations across its single
shared address space. We present a detailed description of the Grappa system,
programming examples using the library interface, and compare performance for
several irregular benchmarks to the Cray XMT, a custom system used to target
the real time graph analytics market.

### 2012-07-23 doc/asplos13/intro.tex
pass on abstract and intro.

Our evaluation of Grappa shows that it runs several graph-crunching applications (classic examples of irregular behavior) very efficiently on a commodity cluster  Our yardstick for comparison is the XMT hardware itself.  Using the same number of processors (in our case cores on a single multicore processor), Grappa is in the same ballpark as the XMT: on some graphs, such as the \checkme{WTF} Grappa is \checkme{2X} faster, while on others, such as the \checkme{WTF2} Grappa is \checkme{2X} slower.  In Section~\ref{sec:results} we explore the factors that underpin this performance.  But most importantly, application performance \emph{scales} with Grappa.  For significantly less real world cost, users can \emph{add} more processors to a commodity cluster and easily outperform the XMT hardware on graph processing, while still saving significant dollars.
% 
% \TODO{Add roadmap here. Luis: do we really want a roadmap here? We have enough about what we have done I think, so we might not need to sell things we plan to do.}

>>>>

Our evaluation of Grappa shows that it runs several graph-crunching
applications (classic examples of irregular behavior) very efficiently on a
commodity cluster. Our yardstick for comparison is the XMT hardware itself.
Using the same number of processors (in our case cores on a single multicore
processor), Grappa is in the same ballpark as the XMT: on some graphs, such as
the \checkme{WTF} Grappa is \checkme{2X} faster, while on others, such as the
\checkme{WTF2} Grappa is \checkme{2X} slower. In Section~\ref{sec:results} we
explore the factors that underpin this performance. But most importantly,
application performance \emph{scales} with Grappa. For significantly less real
world cost, users can \emph{add} more processors to a commodity cluster and
easily outperform the XMT hardware on graph processing, while still saving
significant dollars.

% 
% \TODO{Add roadmap here. Luis: do we really want a roadmap here? We have enough about what we have done I think, so we might not need to sell things we plan to do.}
